Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-18 manuscript/manuscript.tex
Fix wrong fig label
Minor modification in manuscript
Simplify exp density definition on manuscript

\begin{equation}
    \rho(r') = A e^{- \frac{b}{T} (r' - R)} + C,
    \label{eq:density-exp}
\end{equation}

@@

\begin{equation}
    A = \frac{\rho_\text{in} - \rho_\text{out}}{D},
\end{equation}

\begin{equation}
    C = \frac{1}{D}
    \left[\rho_\text{out} \, e^{- \frac{b}{T} (R_1 - R)} -
    \rho_\text{in} \, e^{- \frac{b}{T} (R_2 - R)} \right],
\end{equation}

\begin{equation}
    D = e^{- \frac{b}{T} (R_1 - R)} - e^{- \frac{b}{T} (R_2 - R)},
\end{equation}

\noindent $R$ is the mean Earth radius, $T$ is the thickness of the shell ($T = R_2
- R_1$) and $b$ is a dimensionless constant that determines the variability of the
function: a higher value of $b$ increases the maximum slope of the density function.
On exponential density analysis we will use values of $b$ equal to 1, 2, 5, 10, 30
and 100, in order to cover different kind of exponential density variations, from smooth
to sharp (Fig.~\ref{fig:exp-densities}).

@@

We compute the relative difference between the numerical and analytical results for the
gravitational potential ($V$) and the $g_z$ of the spherical shells detailed in
Table~\ref{tab:shell-models} on each grid detailed in Table~\ref{tab:grids}.
Each shell is assigned with different sinusoidal density functions by changing the
values of $b$ in Eq.~\ref{eq:density-sine} (Fig.~\ref{fig:sine-densities}).
We fixed the distance-size ratio $D$ to the ones obtained for the linear density case
and explored values of $\delta$ ranging from $10^{-4}$ to $1$.
The analytical solution for the potential $V$ can be found on Appendix~\ref{sec:shell}.

\begin{figure}
\centering
\iftwocol{
\includegraphics[width=\linewidth]{figures/sine-densities.pdf}
}{
\includegraphics[width=0.5\linewidth]{figures/sine-densities.pdf}
}
\caption{
    Sinusoidal density functions assigned to each spherical shell in the $\delta$ ratios
    determination.
    Each density function corresponds to a different value of $b$ on
    Eq.~\ref{eq:density-sine}.
}
\label{fig:sine-densities}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/sine-density-diffs.pdf}
\caption{
    Numerical error for different sinusoidal density functions and values of the delta
    ratio.
    The percentage difference values were obtained from the comparison between the
    analytical solution and the numerical approximation of the gravitational fields ($V$
    and $g_z$) generated by the spherical shell with an exponential density function and
    different values of $b$ (Eq.~\ref{eq:density-sine}).
    These comparisons were carried out on every grid defined on Table~\ref{tab:grids},
    making use of the shell models detailed on Table~\ref{tab:shell-models} and
    fixing the distance-size ratio $D$ to the values obtained for the linear density
    case.
    Each curve corresponds to the maximum difference between every shell model with the
    same value of $b$.
    }
\label{fig:delta-exponential}
\end{figure*}

>>>>

\begin{equation}
    \rho(r') = A e^{- \frac{b}{T} (r' - R_1)} + C,
    \label{eq:density-exp}
\end{equation}

@@

\begin{equation}
    A = \frac{\rho_\text{in} - \rho_\text{out}}{1 - e^{-b}},
\end{equation}

\begin{equation}
    C = \rho_\text{in} - A,
\end{equation}

\noindent $T$ is the thickness of the shell ($T = R_2 - R_1$) and $b$ is a dimensionless
constant that determines the variability of the function: a higher value of $b$
increases the maximum slope of the density function.
On exponential density analysis we will use values of $b$ equal to 1, 2, 5, 10, 30
and 100, in order to cover different kind of exponential density variations, from smooth
to sharp (Fig.~\ref{fig:exp-densities}).

@@

We compute the relative difference between the numerical and analytical results for the
gravitational potential ($V$) and the $g_z$ of the spherical shells detailed in
Table~\ref{tab:shell-models} on each grid detailed in Table~\ref{tab:grids}.
Each shell is assigned with different sinusoidal density functions by changing the
values of $b$ in Eq.~\ref{eq:density-sine} (Fig.~\ref{fig:sine-densities}).
The analytical solution for the potential $V$ can be found on Appendix~\ref{sec:shell}.
We fixed the distance-size ratio $D$ to the ones obtained for the linear density case
and explored values of $\delta$ ranging from $10^{-4}$ to $1$.

\begin{figure}
\centering
\iftwocol{
\includegraphics[width=\linewidth]{figures/sine-densities.pdf}
}{
\includegraphics[width=0.5\linewidth]{figures/sine-densities.pdf}
}
\caption{
    Sinusoidal density functions assigned to each spherical shell in the $\delta$ ratio
    determination.
    Each density function corresponds to a different value of $b$ on
    Eq.~\ref{eq:density-sine}.
}
\label{fig:sine-densities}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/sine-density-diffs.pdf}
\caption{
    Numerical error for different sinusoidal density functions and values of the delta
    ratio.
    The percentage difference values were obtained from the comparison between the
    analytical solution and the numerical approximation of the gravitational fields ($V$
    and $g_z$) generated by the spherical shell with an exponential density function and
    different values of $b$ (Eq.~\ref{eq:density-sine}).
    These comparisons were carried out on every grid defined on Table~\ref{tab:grids},
    making use of the shell models detailed on Table~\ref{tab:shell-models} and
    fixing the distance-size ratio $D$ to the values obtained for the linear density
    case.
    Each curve corresponds to the maximum difference between every shell model with the
    same value of $b$.
    }
\label{fig:delta-sine}
\end{figure*}
